Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
Rework model selection.

As introduced in Section~\ref{sec:estimators}, hyper-parameter values set in the
constructor of an estimator determine its behavior. In particular, depending on
the problem, some values produce estimators that are better than others. In this
setting, the problem of \textit{model selection} consists in finding, within
some hyper-parameter space, the combination of hyper-parameter values yielding
an estimator whose performance optimizes some score function on unseen data. For
example, in the case of a decision tree, too small values for the
\texttt{max\_depth} parameter will make the tree to underfit while too large
values will make the tree to overfit the training data. The problem is therefore
to find the best trade-off value in order to maximize the performance of the
tree on unseen data.

In \sklearn, both \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} meta-estimators
implement model selection. They take as inputs an estimator (basic or
complex), a grid of hyper-parameter values, a cross-validation scheme and a
score function. At \texttt{fit}, a \texttt{GridSearchCV} object generates
exhaustively all hyper-parameter combinations from the grid, while a
\texttt{RandomizedSearchCV} instance generates a limited number of combinations
randomly sampled from the grid \citep{bergstra2012}. Then, for each combination, the meta-estimator
fits the given estimator with the corresponding hyper-parameter values and
evaluates its performance through the given cross-validation scheme. Finally,
the best performing model is retained and exposed as a public attribute.

From an API point of view, cross-validation schemes are given as iterator
objects over train and test folds on the training data. The library provides
various such iterators, including K-Fold, Leave-One-Out or shuffled
cross-validation schemes. The score function used by default is the function
provided by the estimator itself. However, the library provides a variety of
score functions that can be used instead, including -- among many others --
accuracy, AUC or $F_\beta$-score for classifiers; $R^2$ score or mean squared
error for regressors; or the Rand Index for clustering estimators.

As an example, the snippet below illustrates how to optimize the hyper-parameter
values of an SVM classifier. It considers an exhaustive exploration of all
hyper-parameter combinations from two distinct grids of parameter values and
maximizes the AUC of the classifier through a 10-fold cross-validation:
\begin{verbatim}
    from sklearn.svm import SVC
    from sklearn.grid_search import GridSearchCV

@@

    clf = GridSearchCV(SVC(), param_grid, scoring="roc_auc", cv=10)
    clf.fit(X_train, y_train)
    y_pred = clf.predict(X_test)
\end{verbatim}
Let us finally note \texttt{GridSearchCV} and \texttt{RandomizedSearchCV}
instances are themselves estimators. In particular, they provide
\texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and \texttt{score}
methods that are all transparently delegated to the best estimator found during
\texttt{fit}, as the example shows.

>>>>

As introduced in Section~\ref{sec:estimators}, hyper-parameters set in the
constructor of an estimator determine its behavior. In particular, depending on
the problem, some hyper-parameters produce estimators that are better than
others. The problem of \textit{model selection} is therefore to find, within
some hyper-parameter space, the best combination of hyper-parameters, with
respect to some user-chosen criterion. For example, in the case of a decision
tree, too small values of the \texttt{max\_depth} parameter will make the tree
underfit while too large values will make the tree overfit the training data.
The problem is therefore to find the best trade-off in order to maximize
the performance of the tree on unseen data.

In \sklearn, model selection is supported in two distinct meta-estimators,
\texttt{GridSearchCV} and \texttt{RandomizedSearchCV}.  They take as inputs an
estimator (basic or composite), whose hyper-parameters must be optimized, and a
hyper-parameter grid, which defines the values to search. Optionally, they can
also take a cross-validation scheme and a score function.  The library provides
various such cross-validation schemes, including K-Fold (default), Leave-One-Out
and Bootstrap. The score function used by default is the \texttt{score} method
provided by the estimator. However, the library provides a variety of
score functions that the user can choose instead, including -- among many others
-- accuracy, AUC, $F_1$-score for classification; $R^2$ score or mean squared
error for regression and the Rand Index for clustering.

\texttt{GridSearchCV} and \texttt{RandomizedSearchCV} differ in the way they
search the hyper-parameter space.  \texttt{GridSearchCV} exhaustively searches
for all hyper-parameter combinations from the grid. This scheme can be expensive
when there are many possible hyper-parameter combinations.
\texttt{RandomizedSearchCV}, on the other hand, only searches for a limited
number of combinations, randomly sampled from the grid. Such scheme has been
shown to work well in practice while considerably reducing the computational
cost \citep{bergstra2012}. For each hyper-parameter combination and each train /
validation split generated by the cross-validation scheme, \texttt{GridSearchCV}
and \texttt{RandomizedSearchCV} fit the base estimator on the training set and
evaluate its performance on the validation set.  In the end, the best performing
model on average is retained and exposed as the public attribute
\texttt{best\_estimator\_}.

As an example, the snippet below illustrates how to optimize the
hyper-parameters of an SVM classifier. It maximizes the $F_1$ score of the
classifier through a 10-fold cross-validation scheme.
\begin{verbatim}
    from sklearn.svm import SVC
    from sklearn.grid_search import GridSearchCV

@@

    clf = GridSearchCV(SVC(), param_grid, scoring="f1", cv=10)
    clf.fit(X_train, y_train)
    y_pred = clf.predict(X_test)
\end{verbatim}
Note that, in the above example, two distinct hyper-parameter grids are
considered. This is because it only makes sense to search for \texttt{gamma}
when \texttt{kernel} is set to \texttt{"rbf"}.  Additionally, we see that
\texttt{GridSearchCV} has a \texttt{predict} method, like any other classifier.
This is because \texttt{GridSearchCV} and \texttt{RandomizedSearchCV} in fact
delegate the \texttt{predict}, \texttt{predict\_proba}, \texttt{transform} and
\texttt{score} methods to the best estimator, thus mimicking its behavior.
